Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-06-29 latex/ms.tex
write 1st para in 2.4, #6

Here we consider the probability that two offspring sampled in the population 1 and 2 share an HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$. For the explanation purpose, we assume equal reproductive potential among parents, although this assumption can be relaxed for most of the case (see details in {\bf Appendix}). $\pi_{\rm HS, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a parent that safely arrives in the population 2 (hereafter, called "migrant"); (ii) the probability that sampled offspring in the population 2 born to a migrant; and (iii) the probability that randomly selected two migrants are identical.

To assess these probabilities, recall there must be two parents of arbitral offspring; the first probability is the sum of father-offspring and mother-offspring relationship, which can be written by $r_{\rm M}M/(r_{\rm S,1}N_{1}) + (1 - r_{\rm M})M/((1-r_{\rm S,1})N_{1})$, where $r_{\rm M}$ and $r_{\rm S,1}$ indicates sex ratio of parents in the migrants and in the whole of the population 1, respectively. Assuming $r_{\rm M} = r_{\rm S,1}$, the probability is simplified as $2M/N_{1}$. Similarly, the second probability is simplified as $2M/N_{2}$, implying the assumption of equal sex ratio in the migrants and the others. Taken together, we obtain
\begin{align}
\pi_{\rm HS,bet} &= \frac{2M}{N_{1}} \frac{2M}{N_{2}} \frac{1}{M} \nonumber\\
&= \frac{4M}{N_{1}N_{2}}.
\label{HS-1}
\end{align}
This form also holds under a flexible setting for the reproductive potential, such as a situation with random variable of $\lambda_{i,1}$ and $\lambda_{j,2}$, as noted in {\bf Appendix}.

@@

@@

\begin{align}
\pi_{\rm PO,bet} &= \frac{2M}{N_{1}} \frac{M}{N_{2}} \frac{1}{M} \nonumber\\
&= \frac{2M}{N_{1}N_{2}}
\label{PO-1}
\end{align}

>>>>

Here, we consider the probability that two offspring sampled in the population 1 and 2 share an HS relationship with an arbitrary mother or father, denoted by $\pi_{\rm HS, bet}$. For the explanation purpose, we assume equal reproductive potential among parents in this section, although this assumption can be relaxed for most of the case (see details in {\bf Appendix}). $\pi_{\rm HS, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a parent that safely arrives in the population 2 (hereafter, called "migrant"); (ii) the probability that sampled offspring in the population 2 born to a migrant; and (iii) the probability that the migrant of a sampled offspring in the population 1 and the migrant of a sampled offspring in the population 2 are identical.

To assess these probabilities, recall there must be two parents of arbitral offspring; the first probability is the sum of father-offspring and mother-offspring relationship, which can be written by $r_{\rm M}M/(r_{\rm S,1}N_{1}) + (1 - r_{\rm M})M/((1-r_{\rm S,1})N_{1})$, where $r_{\rm M}$ and $r_{\rm S,1}$ indicates sex ratio of parents in the migrants and in the whole of the population 1, respectively. Assuming $r_{\rm M} = r_{\rm S,1}$, the probability is simplified as $2M/N_{1}$. Similarly, the second probability is simplified as $2M/N_{2}$, implying the assumption of equal sex ratio in the migrants and the others. The third probability corresponds to the probability that randomly selected two migrants are identical, that is $1/M$. Taken together, we obtain
\begin{align}
\pi_{\rm HS,bet} &= \frac{2M}{N_{1}} \frac{2M}{N_{2}} \frac{1}{M} \nonumber\\
&= \frac{4M}{N_{1}N_{2}}.
\label{HS-1}
\end{align}
This form also holds under a flexible setting for the reproductive potential, such as a situation with random variable of $\lambda_{i,1}$ and $\lambda_{j,2}$, as noted in {\bf Appendix}.

@@

Next, we consider the probability that offspring sampled in the population 1 and a parent sampled in the population 2 share an PO relationship, denoted by $\pi_{\rm PO, bet}$. $\pi_{\rm PO, bet}$ can be partitioned into the three probabilities: (i) the probability that sampled offspring in the population 1 born to a migrant; (ii) the probability that a migrant is sampled; and (iii) the probability that the migrant of a sampled offspring in the population 1 and the migrant sampled in the population 2 are identical.

@@

To assess these probabilities, recall there must be two parents of arbitral offspring; the first probability is the sum of father-offspring and mother-offspring relationship, which can be written by $r_{\rm M}M/(r_{\rm S,1}N_{1}) + (1 - r_{\rm M})M/((1-r_{\rm S,1})N_{1})$, where $r_{\rm M}$ and $r_{\rm S,1}$ indicates sex ratio of parents in the migrants and in the whole of the population 1, respectively. Assuming $r_{\rm M} = r_{\rm S,1}$, the probability is simplified as $2M/N_{1}$. Similarly, the second probability is simplified as $2M/N_{2}$, implying the assumption of equal sex ratio in the migrants and the others. Taken together, we obtain
\begin{align}
\pi_{\rm PO,bet} &= \frac{2M}{N_{1}} \frac{M}{N_{2}} \frac{1}{M} \nonumber\\
&= \frac{2M}{N_{1}N_{2}}
\label{PO-1}
\end{align}
